\documentclass{resume} 

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} 
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Bipin Poudel} 
\address{+1(123) 456-7890 \\ Lincoln, NE} 
\address{\href{mailto:bpoudel2@huskers.unl.edu}{bpoudel2@huskers.unl.edu} \\ 
\href{https://linkedin.com/bipin7}{linkedin.com/bipin7} \\ 
\href{www.bpoudel.com}{www.bpoudel.com}} 

\begin{document}

\begin{rSection}{OBJECTIVE}

{Current graduate seeking internship job in the pharmaceuticals as data analyst.}


\end{rSection}

\begin{rSection}{Education}

{\bf Master of Science (Statistics)}, University of Nebraska-Lincoln \hfill 
{Expected 2024}\\
Relevant Coursework: Biostatistics, Statistical Methods, Categorical Data 
Analysis

{\bf M.Sc. in Statistics}, Tribhuvan University \hfill {2014 - 2017}

{\bf B.Sc. in Statistics}, Tribhuvan University \hfill {2009 - 2013}

\end{rSection}

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & R-programming, Python, SAS
\\
Soft Skills & Friendliness, Communication, Analytical thinking\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Graduate Teaching Assistant} \hfill Aug 2022 - Present\\
Department of Statistics (UNL) \hfill \textit{Lincoln, NE}
 \begin{itemize}
     \item Instructor for STAT 218
 \end{itemize}
 
\textbf{Instructor for Introduction to Statistics} \hfill Aug 2017 - Jan 2022\\
Nepal College of Management \hfill \textit{Kathmandu, Nepa}

\end{rSection} 


\begin{rSection}{Research and Training} 
\begin{itemize}
    \item Masters' dissertation on ‘Analysis of Factors Associated with 
    Perceived Stress Level Among the Masters’ of Science Students of 
    University Campus, Tribhuvan University, Kirtipur, Nepal’ entirely based on 
    primary data.
    \item Training- cum- Workshop on Research and Case Based Teaching Methods as
    a part  of Faculty Development Program (Research Department, Nepal College 
    of Management, 4 – 6 Feb, 2019).
    \item Writing and Analyzing a Business Case as a part of Faculty Development
    Program (Research Department, Nepal College of Management, 31st July, 2019)
\end{itemize}
\end{rSection}

\begin{rSection}{Scholarships and Awards} 
\begin{itemize}
    \item KCRE Excellent Student Thesis Grants Award 2017 provided by Kathmandu
    Center for Research and Education (KCRE) supported by Chinese Academy of 
    Sciences (CAS), Republic of China.
    \item Scholarship for being the student to obtain the highest GPA in M.Sc. 
    2nd Semester provided by Central Department of Statistics, Tribhuvan 
    University., Nepal. 
    \item Awarded scholarship while joining M.Sc for scoring the highest marks 
    in B.Sc provided by Central Department of Statistics, Tribhuvan University.,
    Nepal.

\end{itemize}
\end{rSection}


\end{document}
